---
title: "FSCI 2024 - Data Management"
author: "Kate Schneider"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: html_document
---

### *Overall Objectives*

This script imports and shapes the data from global expert elicitation of interactions between pairs of indicators.
3. Carries out automated literature search for pairs of identified interactions involving at least one governance indicator. The final literature results data set was manually screened for literature in English and relevant to food systems. 

# *Setup and Housekeeping*
```{r setup, warning = FALSE, messages = FALSE, results = "hide", echo = TRUE}
### Setup required to knit this script into a markdown document
    
### Load packages
    # R studio should prompt the installation of any packages not loaded on the instance where this script has been opened
    
    # Data management and multipurpose packages
    library(knitr)
    library(readxl)
    library(stringr)
    library(tidyverse)

### File management
  
    # Set the root folder to the project root so that all file paths are relative to the main project folder
    knitr::opts_knit$set('./')
    
    # Set relative directory paths
      data_in <- here::here("Input data")
      data_out <- here::here("Output data")
      figtab_out <- here::here("Figures & Tables")

### Set preferred options
    
    # Set the treatment of numbers to numerical (avoids scientific notation from showing in results)
    options(scipen = 999)
  
    # Set echo = FALSE for all code chunks will prevent the code from printing in the output file as the default setting (set to TRUE where relevant)
    knitr::opts_chunk$set(echo = FALSE)

### Functions
    
    # Create a "not in" operator
    `%notin%` <- Negate(`%in%`) 
    
```
# *Import and shape the global expert elicitation results*

```{r, warning = FALSE, messages = FALSE, echo = TRUE}
# Import the matrix completed by expert elicitation
  rawdata_all <- readxl::read_xlsx(file.path(data_in,"Interaction_scoring_sheet_All Groups_2024_March.xlsx"), sheet = "Sheet 1 - interaction_scoring_s")
  labels <- readxl::read_xlsx(file.path(data_in,"Interaction_scoring_sheet_All Groups_2024_March.xlsx"), sheet = "Indicator names and labels")

# Start with the first direction of relationship (Column E)
  rawdata <- rawdata_all %>%
    select(c(1:2,4:5)) %>%
    # Label the columns
    rename(theme = 1,
           indicator = 2,
           dependent = 3,
           relationship = 4) %>%
    # Now remove the rows of header information and empty end rows
    filter(row_number() %notin% 1,
           row_number() %notin% 2452:2458) %>%
    # Factor the indicator names and themes, make the relationship numeric
    mutate(theme = as.factor(theme),
           indicator = as.factor(indicator),
           dependent = as.factor(dependent),
           relationship = as.numeric(relationship)) %>%
    # Replace NA with 0 (no relationship)
    mutate(relationship = case_when(is.na(relationship) ~ 0,
                                    TRUE ~ relationship))

# Merge in the short labels for the indicators for figures
  rawdata <- left_join(rawdata, labels, by = "indicator") %>%
    rename(from = short_label,
           from_theme = theme.y) %>%
    select(-c(indicator_order))
  rawdata <- left_join(rawdata, labels, by = c("dependent" = "indicator")) %>%
    rename(to = short_label,
           to_theme = theme) %>%
    select(-c(theme.x, indicator, dependent, indicator_order)) %>%
    relocate(relationship, .after = to_theme) %>%
    mutate(to = as.factor(to),
           from = as.factor(from),
           from_theme = as.factor(from_theme),
           to_theme = as.factor(to_theme))

# Remove the theme columns
  raw_wide <- rawdata %>%
    select(-c(contains("theme"))) %>%
    # Pivot wide
    pivot_wider(names_from = to, 
                values_from = relationship, 
                values_fill = 0) %>%
    relocate("Cost of healthy diet", .after = from)
  
# Confirm indicators are in the correct order
  raw_wide <- left_join(raw_wide, labels, by = c("from" = "short_label")) %>%
    select(-c(indicator, theme))
  raw_wide <- raw_wide[order(raw_wide$indicator_order), ]
  raw_wide <- raw_wide %>%
    select(-c(indicator_order)) %>%
    relocate(`Social capital index`, .before = `Mobile phones per 100 people`)


# Convert to a matrix
# Remove the first column because matrices can only have one class of data
  matrix1 <- as.matrix(raw_wide[, -1]) # eliminate rownames column to get numerical matrix

# Add back the row names
  rownames(matrix1) <- raw_wide$from # assign rownames

# Square and cube the matrix
  matrix2 <- matrix1 %*% matrix1
  matrix3 <- matrix1 %*% matrix1 %*% matrix1

# Reshape the second and third order connections into long data frames
# Create a function to reshape matrix to data frame
  reshapetodf <- function(input_matrix) {
    input <- data.frame(input_matrix) 
    input$from <- row.names(input)   
    input <- input %>%
      pivot_longer(1:50, names_to = "to", values_to = "relationship") %>%
      mutate(to = stringr::str_replace_all(to, "\\.", " "),        
             to = stringr::str_replace_all(to, "   ", " "),
             to = case_when(to == "NCD Protect" ~ "NCD-Protect",
                            to == "NCD Risk" ~ "NCD-Risk",
                            TRUE ~ to)) 
    return(input)
  }

# Execute the function on the matrices
  df_order2 <- reshapetodf(matrix2)
  df_order3 <- reshapetodf(matrix3)

# Add from theme to the long second and third order connections
  rawdata_from <- rawdata %>% select(c("from", "from_theme")) %>% unique()
  df_order2 <- left_join(df_order2, rawdata_from, by = "from") 
  df_order3 <- left_join(df_order3, rawdata_from, by = "from") 

# Add indicator order for from variable
  rawdata <- left_join(rawdata, labels[,c("short_label", "indicator_order")], by = c("from" = "short_label"))
    rawdata <- rawdata %>% rename(from_order = indicator_order)
  df_order2 <- left_join(df_order2, labels[,c("short_label", "indicator_order")], by = c("from" = "short_label"))
    df_order2 <- df_order2 %>% rename(from_order = indicator_order)
  df_order3 <- left_join(df_order3, labels[,c("short_label", "indicator_order")], by = c("from" = "short_label"))
    df_order3 <- df_order3 %>% rename(from_order = indicator_order)

```

$~$

Repeat for the relationships identified in the other direction (Column F)
```{r, warning = FALSE, messages = FALSE, echo = TRUE}
# Load data and clean
  rawdata2 <- rawdata_all %>%
    select(c(1:2,4,6)) %>%
    # Label the columns
    rename(theme = 1,
           dependent = 2,
           indicator = 3,
           relationship = 4) %>%
    # Fix the open budget index name in the dependent column
    mutate(dependent = case_when(dependent == "Open Budget Index" ~ "Open Budget Index Score",
                                 TRUE ~ dependent)) %>%
    # Now remove the rows of header information and empty end rows
    filter(row_number() %notin% 1,
           row_number() %notin% 2452:2458) %>%
    # Factor the indicator names and themes, make the relationship numeric
    mutate(theme = as.factor(theme),
           indicator = as.factor(indicator),
           dependent = as.factor(dependent),
           relationship = as.numeric(relationship)) %>%
    # Replace NA with 0 (no relationship)
    mutate(relationship = case_when(is.na(relationship) ~ 0,
                                    TRUE ~ relationship))

# Merge in the short labels for the indicators for figures
  rawdata2 <- left_join(rawdata2, labels, by = "indicator") %>%
    rename(from = short_label,
           from_theme = theme.y) %>%
    select(-c(indicator_order))
  rawdata2 <- left_join(rawdata2, labels, by = c("dependent" = "indicator")) %>%
    rename(to = short_label,
           to_theme = theme) %>%
    select(-c(1:3)) %>%
    relocate(relationship, .after = to_theme) %>%
    select(-c(indicator_order))
  
  # Remove the theme columns
  raw_wide2 <- rawdata2 %>%
    select(-c(contains("theme"))) %>%
    # Pivot wide
    pivot_wider(names_from = to, 
                values_from = relationship, 
                values_fill = 0) %>%
    relocate("Cost of healthy diet", .after = from) %>%
    filter(!(is.na(from)))
  
# Confirm indicators are in the correct order
  raw_wide2 <- left_join(raw_wide2, labels, by = c("from" = "short_label")) %>%
    select(-c(indicator, theme))
  raw_wide2 <- raw_wide2[order(raw_wide2$indicator_order), ]
  raw_wide2 <- raw_wide2 %>%
    select(-c(indicator_order)) %>%
    relocate(`Social capital index`, .before = `Mobile phones per 100 people`)

# Convert to matrix
  matrix1_v2 <- as.matrix(raw_wide2[, -1]) # eliminate rownames column to get numerical matrix

# Add back the row names
  rownames(matrix1_v2) <- raw_wide2$from # assign rownames

# Square and cube the matrix
  matrix2_v2 <- matrix1_v2 %*% matrix1_v2
  matrix3_v2 <- matrix1_v2 %*% matrix1_v2 %*% matrix1_v2

# Reshape the second and third order connections into long data frames
# Add from theme to the long second and third order connections
  rawdata_from2 <- rawdata2 %>% select(c("from", "from_theme")) %>% unique %>%
    filter(!(is.na(from))) %>%
    collapse::roworderv(neworder = 50)

  df_order2_v2 <- reshapetodf(matrix2_v2) 
  df_order3_v2 <- reshapetodf(matrix3_v2) 

# Add from theme to the long second and third order connections
  rawdata_from_v2 <- rawdata2 %>% select(c("from", "from_theme")) %>% unique() %>%
    filter(!(is.na(from)))
  df_order2_v2 <- left_join(df_order2_v2, rawdata_from, by = "from") 
  df_order3_v2 <- left_join(df_order3_v2, rawdata_from, by = "from") 
  
# Add indicator order variable for the from variable
  rawdata2 <- left_join(rawdata2, labels[,c("short_label", "indicator_order")], by = c("from" = "short_label"))
    rawdata2 <- rawdata2 %>% rename(from_order = indicator_order)
  df_order2_v2 <- left_join(df_order2_v2, labels[,c("short_label", "indicator_order")], by = c("from" = "short_label"))
    df_order2_v2 <- df_order2_v2 %>% rename(from_order = indicator_order)
  df_order3_v2 <- left_join(df_order3_v2, labels[,c("short_label", "indicator_order")], by = c("from" = "short_label"))
    df_order3_v2 <- df_order3_v2 %>% rename(from_order = indicator_order)

```

Create a new data frame that merges column E and F information, ensuring all relationships identified are included, and preserving the directionality of the relationships.  
```{r, warning = FALSE, messages = FALSE, echo = TRUE}

# Create combined matrix by adding matrix 1 (column E) to matrix1_v2 (column F)

# Add the matrix elements together into a new matrix
  combo_matrix_keepbidirect <- matrix1 + matrix1_v2

# Now any cells with causality in both directions have a value of 2 - replace with 1
  combo_matrix <- combo_matrix_keepbidirect
  combo_matrix[combo_matrix==2] <- 1

# Reshape to data frame, fixing indicator names that lose punctuation in the matrix conversion
  combo_df <- reshapetodf(combo_matrix) %>%
    mutate(to = str_replace_all(to, "Conservation of genetic resources  plants", "Conservation of genetic resources, plants")) %>%
    mutate(to = str_replace_all(to, "Conservation of genetic resources  animals", "Conservation of genetic resources, animals")) %>%
    mutate(to = str_replace_all(to, "Minimum dietary diversity  women", "Minimum dietary diversity, women")) %>%
    mutate(to = str_replace_all(to, "Minimum dietary diversity  child", "Minimum dietary diversity, child")) %>%
    mutate(to = str_replace_all(to, "Ultra processed food sales", "Ultra-processed food sales"))
  
  combo_df_keepbidirect <- reshapetodf(combo_matrix_keepbidirect)  %>%
    mutate(to = str_replace_all(to, "Conservation of genetic resources  plants", "Conservation of genetic resources, plants")) %>%
    mutate(to = str_replace_all(to, "Conservation of genetic resources  animals", "Conservation of genetic resources, animals"))  %>%
    mutate(to = str_replace_all(to, "Minimum dietary diversity  women", "Minimum dietary diversity, women")) %>%
    mutate(to = str_replace_all(to, "Minimum dietary diversity  child", "Minimum dietary diversity, child")) %>%
    mutate(to = str_replace_all(to, "Ultra processed food sales", "Ultra-processed food sales"))

# Add from theme 
  combo_df <- left_join(combo_df, rawdata_from, by = "from") 
  combo_df_keepbidirect <- left_join(combo_df_keepbidirect, rawdata_from, by = "from") 

# Square and cube the matrix
  matrix2_combo <- combo_matrix %*% combo_matrix
  matrix3_combo <- combo_matrix %*% combo_matrix %*% combo_matrix

# Reshape matrices to data frame
  df_order2_combo <- reshapetodf(matrix2_combo) 
  df_order3_combo <- reshapetodf(matrix3_combo) 

# Add from theme to the long second and third order connections
  df_order2_combo <- left_join(df_order2_combo, rawdata_from, by = "from")
  df_order3_combo <- left_join(df_order3_combo, rawdata_from, by = "from") 
  
# Add indicator order variable for the from variable
  combo_df <- left_join(combo_df, labels[,c("short_label", "indicator_order")], by = c("from" = "short_label"))
    combo_df <- combo_df %>% rename(from_order = indicator_order)
  combo_df_keepbidirect <- left_join(combo_df_keepbidirect, labels[,c("short_label", "indicator_order")], by = c("from" = "short_label"))
    combo_df_keepbidirect <- combo_df_keepbidirect %>% rename(from_order = indicator_order)
  df_order2_combo <- left_join(df_order2_combo, labels[,c("short_label", "indicator_order")], by = c("from" = "short_label"))
    df_order2_combo <- df_order2_combo %>% rename(from_order = indicator_order)
  df_order3_combo <- left_join(df_order3_combo, labels[,c("short_label", "indicator_order")], by = c("from" = "short_label"))
    df_order3_combo <- df_order3_combo %>% rename(from_order = indicator_order)
    
# Clean up
  rm(raw_wide, raw_wide2)
  
# Bring back theme 
  combo_df_keepbidirect <- left_join(combo_df_keepbidirect, rawdata[,c("to", "to_theme")], by = "to") %>% unique()

```

$~$

Combine matrices keeping lowest order connection for each pair.
```{r, warning = FALSE, messages = FALSE, echo = TRUE}
  # Replace all values in matrix 2 with 2, and matrix 3 with 3 (indicating the order of connection between each pair of variables instead of the number of pathways connecting them)
    matrix2_combo[matrix2_combo > 0] <- 2
    matrix3_combo[matrix3_combo > 0] <- 3
  
    matrix_combined_combo <- ifelse(combo_matrix == 1, combo_matrix, matrix2_combo) # keep 1's from matrix 1, otherwise use the values of matrix 2
    matrix_combined_combo <- ifelse(matrix_combined_combo == 0, matrix3_combo, matrix_combined_combo) # now use the values from matrix 3 only if the combo matrix cell is 0 (no first or second order connection)
  
  # Reshape
    matrix_combined_df_combo <- reshapetodf(matrix_combined_combo) %>%
      mutate(from = as.factor(from))  %>%
      mutate(to = str_replace_all(to, "Conservation of genetic resources  plants", "Conservation of genetic resources, plants")) %>%
      mutate(to = str_replace_all(to, "Conservation of genetic resources  animals", "Conservation of genetic resources, animals"))  %>%
      mutate(to = str_replace_all(to, "Minimum dietary diversity  women", "Minimum dietary diversity, women")) %>%
      mutate(to = str_replace_all(to, "Minimum dietary diversity  child", "Minimum dietary diversity, child")) %>%
      mutate(to = str_replace_all(to, "Ultra processed food sales", "Ultra-processed food sales"))
  
  # Bring back theme 
    matrix_combined_df_combo <- left_join(matrix_combined_df_combo, rawdata[,c("from", "from_theme")], by = "from") %>% unique()
    matrix_combined_df_combo <- left_join(matrix_combined_df_combo, rawdata[,c("to", "to_theme")], by = "to") %>% unique()
    
  # Bring back variable order for from
    matrix_combined_df_combo <- left_join(matrix_combined_df_combo, labels[,c("short_label", "indicator_order")], by = c("from" = "short_label"))
    matrix_combined_df_combo <- matrix_combined_df_combo %>% rename(from_order = indicator_order)

```

$~$

Save the datasets
```{r, warning = FALSE, messages = FALSE, echo = TRUE}
# Rename data frames for interpretability and subsequent analysis
    Interactions_ExpertElicit_Direct <- combo_df
    Interactions_ExpertElicit_DirectMatrix <- combo_matrix
    Interactions_ExpertElicit_AdjacencyMatrix <- matrix_combined_df_combo
    Interactions_ExpertElicit_Bidirect <- combo_df_keepbidirect

# Save data sets in format needed for network diagrams
    save(Interactions_ExpertElicit_Direct, Interactions_ExpertElicit_DirectMatrix,
         Interactions_ExpertElicit_AdjacencyMatrix, Interactions_ExpertElicit_Bidirect,
         file = file.path(data_out, "Interactions_ExpertElicititation.RData"))
    
# Clean up
    rm(df_order2, df_order2_combo, df_order2_v2, df_order3, df_order3_combo, df_order3_v2, duplicate_pairs, matrix_combined_combo, matrix1, matrix1_v2, matrix2, matrix2_v2, matrix2_combo, matrix3, matrix3_combo, matrix3_v2, rawdata, rawdata_all, rawdata_from, rawdata_from2, rawdata_from_v2, combo_matrix_keepbidirect, rawdata2, combo_df, combo_matrix, matrix_combined_df_combo, combo_df_keepbidirect)
    

```

Now export the combined matrix pairs into the literature search analysis as they will form the basis of the first step in the search (naive search).
```{r, warning = FALSE, messages = FALSE, echo = TRUE}

# Develop a data frame of the indicator pairs
  indicatorpairs <- Interactions_ExpertElicit_AdjacencyMatrix %>%
    filter(relationship == 1) %>%
    filter(from != to) %>% ## Remove identity 
    filter(from_theme == "Governance" | to_theme == "Governance") %>%
    select(from, to)

# Now remove duplicate pairings (regardless of their order in to or from columns)
# function(x) is defining a function that sorts the elements of each row of the data frame data, and then concatenates them into a single string with "-" as the separator. This is done for each row of the data frame using apply, resulting in a vector of sorted pairs of "from" and "to" values for each row.
  sorted_pairs <- apply(indicatorpairs, 1, function(x) paste(sort(x), collapse = " AND "))
    
# Create a boolean column that marks the second occurence of a pair as a duplicate
  duplicate_pairs <- as.data.frame(duplicated(sorted_pairs) | duplicated(sorted_pairs, fromLast = TRUE))
  duplicate_pairs <- duplicate_pairs %>%
    rename(duplicate = 1)
  
# Add in the duplication information to the sorted pairs
  searchterms <- cbind(sorted_pairs, duplicate_pairs) %>%
    # Drop the duplicate rows
    filter(duplicate != TRUE) %>%
    # Rename 
    rename(naive_search = 1) %>%
    select(-c(duplicate))

# Now split back up into multiple columns
   searchterms <- searchterms %>%
     tidyr::separate(naive_search, c("concept 1", "concept 2"), sep = " AND ")
    
  # Manually revise some search terms
    # Create a find and replace function:
    findreplace <- function(x, y, data) {
      for (i in seq_along(x)) {
        data <- mutate(data, across(everything(), ~ gsub(x[i], y[i], .x)))
      }
      return(data)
    }
   
    changefrom <- c("NCD-Protect", "NCD-Risk", "Food system pathway", "All 5 food groups")
    changeto <- c("dietary protection from non-communicable disease", "dietary risk of non-communicable disease", "food system transformation pathway", "consuming all essential food groups")
    searchterms <- findreplace(changefrom, changeto, searchterms) 
    searchterms <- searchterms %>% mutate(across(everything(), tolower))
    changefrom <- c("milan", "gdp")
    changeto <- c("Milan", "GDP")
    searchterms <- findreplace(changefrom, changeto, searchterms) 
    
# Save to the literature search folder as .csv
    writexl::write_xlsx(searchterms, path = file.path(data_in, "Search terms.xlsx"), col_names = TRUE)
   
```
